Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-08 Writing/CEA_2nd_round/replies_rev_1.rmd
final changes before Dave's review

---
title: "Reply to Reviewer #1"
author: Shunkei Kakimoto
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
---

# Comments:

@@

<span style="color:blue">  
Yes, we agree with your point, and we have decided to simply drop it from our highlights.

@@

@@

We have moved an example of causal tree (previously in seciton 2.3), but decide to keep the explanation of how CF works. The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations. To this core objective, ML simulation is our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give too much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal. However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Insted, we believe that it is better to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted. Therefore, we kept 2.3 and 2.4 (in the previous round) in the current manuscript.

@@

In rereponse to this comments, we made several changes.

@@

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our current manuscript is appropriate and it is hard for us to further slim down the section. Moreover, we believe we no longer have any redundancy in this section.

**4. What is the unit of the topographical slope？ (line 131)**
<span style="color:blue">

It is degree. The unit is now provided in the description of the figure in Appendix A. Please not that this example is just for illustrating how CF works.

**5. There are 3 numbers in each small frame of Figure 1, please describe the meaning of each number in detail in the figure caption. (line 137)**
<span style="color:blue">

The explanation for those numbers are added as a footnote to the figure (Figure <span style = "color: blue;"> Shun, figure number </span>). 
</span>

@@

**7. What are the exact number and proportion of test set training sets? (line 192)**
<span style="color:blue">

We aplogogize that we are not clear on this respect.

Trainign dataset and test dataset are completely separate. For a given simulation round, training dataset in another round of simulation acts as a "test" dataset. The "test" dataset are created independently from one another and are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$. Therefor, in MC simulations, a dataset in a given simulation serves as a train data, and served as a test data for another simulation round. The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters within a given simulation round.

@@

"For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset. For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset. This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$). Furtehr, each of the "train" datasets are generated independet of one another. Thefore, for a particular simulation round, the dataset in any of the other simualtions can serve as a valid test dataset. This practice avoid creating another set of 1000 simulations fields unnecessarily."

@@

<span style="color:blue">  
We realized that section 3.1 has also a bad title. Therefore, we changed it to "Training Models and Estimating Site-specific EONRs". Further, the title of sections 3.2.1 and 3.2.2 were changed to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively. 
</span>

@@

<span style="color:blue">  
The title of 4.1 was changed to "Comparison of EONR estimation accuracy" to reflect its contents. The title of section 4.2 was changed to "The relationship between yield and EONR prediction performances". 
</span>

@@

As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1). Consequently, I do not think that visualizing the CNN results provide any meaningful implications to understand its performance of EONR estimation performance.

+ I added the explanation for not showing CNN results in Figures 8,9, and 10. ("CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively")
</span>

@@

<span style="color:blue">  
+ run simulations on training dataset, and report the results.
</span>

>>>>

---
title: "Reply to Reviewer #1"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: word_template_format.docx
---

Thank you so much for your comments. By addressing them, we believe the manuscript is improved significantly. You can find our replies to your comments. Your comments are in bold, and out replies are in a regular font.

<br>

@@

<span style="color:blue">  
Yes, we agree with your point, and we have decided to simply drop it from our highlights.
</span>

<br>

@@

<br>

@@

We have moved an example of causal tree (previously in seciton 2.3), but decide to keep the explanation of how CF works. The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations. To this core objective, ML simulation is our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give too much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal. However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Insted, we believe that it is better to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted. Therefore, we kept 2.3 and 2.4 (in the previous round) in the current manuscript.
</span>

<br>

@@

<span style="color:blue">  
In rereponse to this comments, we made several changes.

@@

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our current manuscript is appropriate and it is hard for us to further slim down the section. Moreover, we believe we no longer have any redundancy in this section. 
</span>

<br>

**4. What is the unit of the topographical slope？ (line 131)**

<span style="color:blue">  
It is degree. The unit is now provided in the description of the figure in Appendix A. Please not that this example is just for illustrating how CF works.
</span>

<br>

**5. There are 3 numbers in each small frame of Figure 1, please describe the meaning of each number in detail in the figure caption. (line 137)**

<span style="color:blue">  
Explanations for those numbers are added as a footnote to the figure. The figure is now in the appendix and called Figure A.1. 
</span>

<br>

@@

<br>

**7. What are the exact number and proportion of test set training sets? (line 192)**

<span style="color:blue">  
We aplogogize that we are not clear on this respect.

Trainign dataset and test dataset are completely separate. For a given simulation round, the training dataset in another round of simulation acts as a "test" dataset. These datasets are created independently from one another and are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$. Therefor, in MC simulations, the dataset in a given simulation serves as a train dataset, and served as a test data for another simulation round. The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters within a given simulation round.

@@

"For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset. For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset. This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$). Furtehr, each of the "train" datasets are generated independet of one another. Thefore, for a particular simulation round, the dataset in any of the other simualtion rounds can serve as a valid test dataset. This practice avoid creating another set of 1000 simulations fields unnecessarily."
</span>

<br>

@@

<span style="color:blue">  
We realized that section 3.1 also had a uninformative title. Therefore, we changed it to "Training Models and Estimating Site-specific EONRs". Further, the title of sections 3.2.1 and 3.2.2 were changed to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively. 
</span>

<br>

@@

<span style="color:blue">  
The title of 4.1 was changed to "Comparison of EONR estimation accuracy" to reflect its contents. The title of section 4.2 was changed to "The relationship between yield and EONR prediction performances". They acurrately reflect what they describe.
</span>

<br>

@@

As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1). Therefore, we thought that visualizing the CNN results are not insightful. However, we have decided to include CNN results to Figures 8, 9, and 10 in the previous version. The figures are now Figures 3, 4, and 5.

<br>

@@

<span style="color:blue">  
Shun is running simulations on training dataset and will report the results.
</span>

<br>

### 2022-02-08 Writing/CEA_2nd_round/replies_rev_2.rmd
final changes before Dave's review

---
title: "Reply to Reviewer #2"
author: Shunkei Kakimoto
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template.docx
---

@@

**2. Fig, 1. Indicate units for slope and EC in title.**
<span style="color:blue"> 
The units of slope and EC are added in the description, which can be found in Appendix A.
</span>

@@

+ I removed Table 1. Instead, I explained about those parameters in section 3.1.3. I added units of "ymax" and "$\varepsilon$" to Figure 3.
</span>

@@

**7. P. 29 l 449: Points are clustered much more tightly about the 1-to-1 line much for CF-base than RF and BRF. (remove much)**
<span style="color:blue">  
We removed "much" from the sentence.
</span>

**8. Table 3. Provide units.**
<span style="color:blue">

The unit (kg/ha) was provided in Table <span style = "color: blue;"> Shun say the table number here </span>. Similarly, units are provided to other result tables.
</span>

>>>>

---
title: "Reply to Reviewer #2"
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template_format.docx
---

@@

**2. Fig, 1. Indicate units for slope and EC in title.**

<span style="color:blue"> 
The units of slope and EC are added in the description, which can be found in Appendix A.
</span>

@@

Units are added to the table and figure where applicable. They are now in Appendix C.
</span>

@@

**7. P. 29 l 449: Points are clustered much more tightly about the 1-to-1 line much for CF-base than RF and BRF. (remove much)**

<span style="color:blue">  
We removed "much" from the sentence.
</span>

**8. Table 3. Provide units.**

<span style="color:blue"> 
The unit (kg/ha) was provided in the table (it is now Table 2). Similarly, units are provided to the other result tables.
</span>

### 2022-02-08 Writing/manuscript_cea.rmd
final changes before Dave's review

For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset. For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset. This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$). Furtehr, each of the "train" datasets are generated independet of one another. Thefore, for a particular simulation round, the dataset in any of the other simualtions can serve as a valid test dataset. This practice avoid creating another set of 1000 simulations fields unnecessarily.

@@

We examined the use of CF-base for site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF-base consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. We also showed that the model's yield prediction accuracy was uncorrelated with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map.

>>>>

For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset. For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset. This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$). Furtehr, each of the "train" datasets are generated independet of one another. Thefore, for a particular simulation round, the dataset in any of the other simualtion rounds can serve as a valid test dataset. This practice avoid creating another set of 1000 simulations fields unnecessarily.

@@

We examined the use of CF for site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF. It is recommended that BRF is used in place of RF according to out results. Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.

We also showed that the model's yield prediction accuracy has little to do with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map. Many studies seek to predict yield level accurately using deep learning methods. However, the usefulness of such models may be questionable when it comes to using them for making management decisions. Further examinations into this issues is warranted.
